
~\vspace{3cm}

\begin{thebibliography}{99}

\bibitem{Mathematica},
Steven Wolfram (2000), \\
"The Mathematica Book", Fourth edition, \\
Cambridge University Press, \\
\href{http://www.mathematica.com/}{"http://www.mathematica.com/"}.

\bibitem{feynarts} J.~K\"ublbeck, M.~B\"ohm and A.~Denner, 
Comp.~Phys.~Comm.~{\bf 60} (1990) 165.\\
\href{http://www.feynarts.de/}{"FeynArts web site"}.

%\cite{Drinkard:1981dr}
\bibitem{Drinkard:1981dr}
R.~D.~Drinkard and N.~K.~Sulinski,
``Macsyma: A Program For Computer Algebraic Manipulation (Demonstrations And Analysis),''
NUSC-6401
\href{http://www.slac.stanford.edu/spires/find/hep/www?r=nusc-6401}{"SPIRES entry"}.

\bibitem{yeh}
E.~Yehudai and A.~C.~K.~Hsieh,
{\sl HIP\/} --- Symbolic  High-Energy Physics Calculations, \\
SLAC-PUB-~{\bf 5576} July 1991.

%\cite{Tarasov:1997kx}
\bibitem{Tarasov:1997kx}
O.~V.~Tarasov,
``Generalized recurrence relations for two-loop propagator integrals with  arbitrary masses,''
Nucl.\ Phys.\ B {\bf 502} (1997) 455
\href{http://xxx.lanl.gov/abs/hep-ph/9703319}{"arXiv:hep-ph/9703319"}.
%%CITATION = HEP-PH 9703319;%%

%\cite{Mertig:1998vk}
\bibitem{Mertig:1998vk}
R.~Mertig and R.~Scharf,
``TARCER: A mathematica program for the reduction of two-loop propagator  integrals,''
Comput.\ Phys.\ Commun.\  {\bf 111} (1998) 265
\href{http://xxx.lanl.gov/abs/hep-ph/9801383}{"arXiv:hep-ph/9801383"}.
%%CITATION = HEP-PH 9801383;%%

%\cite{Gasser:1984gg}
\bibitem{Gasser:1984gg}
J.~Gasser and H.~Leutwyler,
``Chiral Perturbation Theory: Expansions In The Mass Of The Strange Quark,''
Nucl.\ Phys.\ B {\bf 250} (1985) 465.
%%CITATION = NUPHA,B250,465;%%

%\cite{'tHooft:1978xw}
\bibitem{'tHooft:1978xw}
G.~'t Hooft and M.~J.~Veltman,
``Scalar One Loop Integrals,''
Nucl.\ Phys.\ B {\bf 153} (1979) 365.
%%CITATION = NUPHA,B153,365;%%

\bibitem{ansgar}
A.~Denner,  "Techniques for the Calculation of Electroweak 
Radiative Corrections at the One-Loop Level and Results for 
$W$-Physics at LEP200", 
to appear in {\sl Fortschritte der Physik 1992, 41} 
and references therein.

\bibitem{feyncalc} R.~Mertig, M.~B\"ohm, and A.~Denner,
Comp.~Phys.~Comm.~{\bf 64} (1991) 345. 

\bibitem{west}
Comp.~Phys.~Comm~{\bf 77} (1993) 286-298.

\bibitem{Ol91} 
G.~J.~van Oldenborgh, "FF -- a package to evaluate one-loop Feynman diagrams",
Comp.~Phys.~Comm.~{\bf 66} (1991) 1.\\
Z.\ Phys.\ C {\bf 46} (1990) 425,\\
\href{http://ccdb3fs.kek.jp/cgi-bin/img_index?9004168}{"Scanned version from KEK"}.

%\cite{Hahn:1998yk}
\bibitem{Hahn:1998yk}
T.~Hahn and M.~Perez-Victoria,
``Automatized one-loop calculations in four and D dimensions,''
Comput.\ Phys.\ Commun.\  {\bf 118} (1999) 153
\href{http://xxx.lanl.gov/abs/hep-ph/9807565}{"arXiv:hep-ph/9807565"}.
%%CITATION = HEP-PH 9807565;%%

%\cite{Breitenlohner:hr}
\bibitem{Breitenlohner:hr}
P.~Breitenlohner and D.~Maison,
``Dimensional Renormalization And The Action Principle,''
Commun.\ Math.\ Phys.\  {\bf 52} (1977) 11.
%%CITATION = CMPHA,52,11;%%

%\cite{Martin:1999cc}
\bibitem{Martin:1999cc}
C.~P.~Martin and D.~Sanchez-Ruiz,
``Action principles, restoration of BRS symmetry and the renormalization  group equation for chiral non-Abelian gauge theories in dimensional
renormalization with a non-anticommuting gamma(5),''
Nucl.\ Phys.\ B {\bf 572} (2000) 387
[arXiv:hep-th/9905076].
%%CITATION = HEP-TH 9905076;%%

\bibitem{cvit}
P.Cvitanovic, Phys.~Rev.~D~{\bf 14} (1976) 1536.

\bibitem{kry}
A.P.~Kryukov and A.Ya.~Rodionov, Comp.~Phys.~Comm.~{\bf 48} (1988) 
327.

\bibitem{laut}
Matthias Jamin and E.~Lautenbacher, 
"TRACER, A Mathematica Package for $\gamma$-Algebra in Arbitrary Dimensions",
preprint Technische Universit\"at M\"unchen, TUM-T31-20/91.

\bibitem{Wo79} S.~Wolfram, "MACSYMA Tools for Feynman Diagram Calculations",
{\sl Proceedings of the 1979 MACSYMA Users Conference}.

\bibitem{PHI} Frederik Orellana, "PHI, a Mathematica package for doing loop calculations in Chiral Perturbation Theory", {\it in preparation}, \href{http://www.feyncalc.org/phi/}{"PHI web site"}.

%\cite{Ecker:1992jh}
\bibitem{Ecker:1992jh}
G.~Ecker,
%``Chiral perturbation theory,''
CERN-TH-6660-92
%\href{http://www.slac.stanford.edu/spires/find/hep/www?r=cern-th-6660-92}{SPIRES entry}
{\it To be published in the proceedings of 4th Hellenic School on Elementary Particle Physics, Corfu, Greece, 2-20 Sep 1992 and Lectures given at
Cargese Summer School on Quantitative Particle Physics, Cargese, 20 Jul-1 Aug 1992}.

%\cite{Hahn:2000kx}
\bibitem{Hahn:2000kx}
T.~Hahn,
%``Generating Feynman diagrams and amplitudes with FeynArts 3,''
Comput.\ Phys.\ Commun.\  {\bf 140} (2001) 418
[arXiv:hep-ph/0012260].
%%CITATION = HEP-PH 0012260;%%
\href{http://www.feynarts.de/}{"FeynArts web site"}.

\end{thebibliography}
