\sectionmark{Preface}
\section*{Preface}

This book is for practitioners of calculations in perturbative QCD,
the Standard Model, Chiral Perturbation Theory and other theories.
The intention is to serve both educational as well as research purposes.
This is reflected in the layout of the parts.
The first part is a tutorial-like introduction with many small examples.
It is necessarily of a rather technical character and should prepare the
reader for doing real physics calculations.
The second part contains a variety of example calculations from textbook
%to research level. The interested student will find here calculations calculations
to research level. The interested student will find here calculations 
from the literature worked through in a detail not found elsewhere.
The researcher will find calculations that should provide a starting point
for calculations of his or her own research.
The third part is a reference guide, listing all important functions,
also with many small examples.
%The user is assumed to know Quantum Field Theory and have some understanding of \mma.
%It is strongly recommended to study the \mma book \cite{Mathematica} by
%Stephen Wolfram before starting with \fc.

Over the years, the detailed course of and motivation for the development of \fc has
changed somewhat both in scope and focus. The reasons are the different research
interests of the two authors, the relative slowness of \mma and the rapid development of
multi-loop calculations carried out with FORM and programs based on FORM 
\cite{Vermaseren:2000nd, Hahn:1998yk}, which are  more suited for very large scale calculations.
Also \fc has tools to interact with FORM. This is particularly useful if the CPU time is
an issue or if truly large expressions occur and a very efficient way to handle those 
expressions is needed. FORM is very much suited for this task. 
On the other hand, general purpose computer algebra systems like \mma have more flexibility in their user interface and one can use the already provided libraries for operations like
integration and series expansions and more mathematical tasks.
%3) the rapid development of the raw computing power of hardware. 
%As a consequence the focus has moved away from providing cutting edge results of multi-loop
%calculations in the Standard Model and in QCD. 
One focus has been to explore other types of calculations than the evaluation of Feynman
diagrams, e.g. complex algebraic manipulations of quantum fields and lagrangians, traditionally done by hand only.
Such calculations have become feasible because of the steep increase of the computing
power of commodity hardware.

Despite the motivations driving development, the central vision remains largely the same: 
\fc was conceived as and continues to be developed as a general-purpose, relatively easy to use,
modular toolbox for quantum field theory calculations. 
Dirac algebra utilities, Lorentz and Color algebra manipulation capabilities, 
functional derivation utilities, integral and other tables have been cleanly 
separated off in distinct functions which 
do well-defined operations.
Such basic functions can then be used  on a higher level to build sophisticated model dependent functions.

In the following we list what we consider the most important general principles that the \fc
project strives to promote:
%%SOFAR

\begin{itemize}

%
%\item{{\bf Standardization.} In order to reuse code, clear standards should be formulated,
%thoroughly documented and followed. The aim should be to reach common standards with
%other similar or related projects (using other programming languages) for fields, lagrangians,
%Lorentz-vectors, etc. in the end allowing easy comparison of calculations of the same process.}

\item{{\bf Systematic knowledge build-up.} In physics calculations, errors due to typos or
other trivial mistakes are not acceptable, therefore the code used should be as thoroughly
checked as possible by as many people as possible. This implies openness and adherence to
standards. It is proposed to build up a repository of lagrangians, amplitudes and integrals,
stored in a standardized electronic form.}

%\item{{\bf Algorithm optimization.} The more people using (an implementation of) an algorithm,
%the better the chances of improving (the implementation of) it.}

\item{{\bf Fast prototyping.} Quickly trying out new quantum field theory models should be made
easier by using the building blocks provided by a clear standardization as well as a set of
functions for the most common calculational tasks.}

\item{{\bf Checks.} Calculations should, when possible, be performed by different methods.
Thus, \fc should be used to check hand calculations or the results of other programs and
vice versa.}

\end{itemize}

%Notice in this connection that the standards put forth in this document (and in the code) are what
%the authors consider to be the most general but still useful standards for doing quantum fields
%theory with \mma. This means that standards are to be considered as relatively fixed, but not that
%they cannot be changed, given good enough reasons.

From all of the above it should be clear that we consider interaction with users to be crucial
for the further evolving of \fc. Therefore, suggestions and in particular
code contributions are warmly welcomed. Smaller contributions can be contributed
on the web site \href{http://www.feyncalc.org/}{http://www.feyncalc.org/}; 
larger contributions should be coordinated with the developers.
Though much testing of the code has been done, there is absolutely no claim that
\fc is bug-free. You should be sceptical about the results, and when you are sure the
program  returns a wrong answer, you are encouraged to report it via the web site
\href{http://www.feyncalc.org/}{http://www.feyncalc.org/}.

\subsection*{Version History}

The roots of \fc go back to 1987. 
During a stay as a graduate student in Albuquerque, New Mexico, Rolf Mertig learned to program in Macsyma \cite{Drinkard:1981dr} from the experts Stanly Steinberg and Michael Wester. Back to Germany, 
elementary particle physicists needed automation of the calculation of Feynman diagrams of eletroweak 
processes to one loop. The algorithms were partially developed together with 
Ansgar Denner and Manfred B\ODoubleDot{}hm and implemented in a 
purely functional way by Rolf Mertig during the years 1987 - 1989. 

The basic idea was to have general functions for some of the more mechanical parts of the diagram calculations, generalizable tools for use in calculations of different 1-loop processes, especially 1\(\rightarrow \)2 and 2\(\rightarrow \)2 processes. These included tools for:

\begin{itemize}

\item{Lorentz algebra.
\({g^{\Mvariable{\mu \nu }}}\multsp {p_{\mu }}
\multsp \rightarrow \multsp {p^{\nu }}
\multsp ,\multsp \multsp\)
\({g^{\Mvariable{\alpha \beta }}}{g_{\Mvariable{\alpha \beta }}}
   \multsp \rightarrow \multsp D\multsp \cdots\),}

\item{Dirac algebra.
\({{\gamma }^{\alpha }}\multsp {{\gamma }^{\nu }}
{{\gamma }_{\alpha }}\multsp \rightarrow \multsp 
(2-n)\multsp {{\gamma }^{\nu }},\multsp \multsp \)
\(\overvar{v}{\_}(p,m)\multsp 
\bps\)  \(\rightarrow \) - m \(\overvar{v}{\_}(p,m)\multsp \cdots\),}

\item{Passarino-Veltman tensor integral decomposition.
Applications of these tools included complete 1-loop processes in the Standard Model,
\({e^+}{e^-}\multsp \rightarrow 
\multsp Z\multsp H\multsp \),  \(\multsp {e^+}{e^-}\multsp \rightarrow \)
\(\multsp {W^+}{W^-}\multsp \)
and the 2-loop photon self-energy in QED.}

\end{itemize}

However, at the end of 1989 several problems showed up with the Macsyma implementation. The purely functional programming style proved to be difficult to debug and, in fact, inappropriate. The rudimentary pattern matcher in Macsyma was not useful. There was no way to incorporate new functions easily into the whole Macsyma system, and no possibility of providing online documentation. Furthermore, Macsyma's memory managment ("garbage collection") was slow when handling large expressions.

In early 1990 it became clear that \mma was a much more natural programming environment for \fc.

\subsubsection*{1990-1991 : The first version  of \fc in \mma}

In 1990, user-friendly  packages were built with extended automatic capabilities (\mb{OneLoop}, \mb{OneLoopSum}), and SU(3) algebra capabilities were added (\mb{SU3Simplify}).

In 1991 initial documentation was written and the program was made available on anonymous ftp-servers: mathsource.wolfram.com and canc.can.nl.

Applications from 1990 - 1996  included:

\begin{itemize}

\item 1-loop 2 \(\rightarrow \)2 processes in the Standard
Model, such as:

\({\rm gg}\multsp \rightarrow \multsp 
{\rm t \overline{t}} \multsp , \multsp \multsp
{{\rm e}^+}{{\rm e}^-}\multsp \rightarrow \multsp {\rm Z}\multsp {\rm H}\multsp, \multsp \multsp
%{{\rm W}^+}{{\rm W}^-}\multsp \)\(\rightarrow \) \({{\rm W}^+}{{\rm W}^-}\multsp, \multsp \multsp
{\rm gg} \rightarrow {\rm t\bar{t}} \),

\item background field gauge calculations,

\item high-energy approximation of \(\multsp{{\rm e}^+}
{{\rm e}^-}\multsp \rightarrow \multsp {{\rm W}^+}{{\rm W}^-}\multsp \),

\item  2-loop Standard Model self-energies.

\end{itemize}

No real attempt was made to provide tools for tree-level calculations. 
For this purpose other programs appeared, among them another  \mma package, \hip \cite{yeh}, developed at SLAC, 
CompHEP \cite{Pukhov:1999gg}, and of course FORM \cite{Vermaseren:2000nd}.

\subsubsection*{1992-1995 : \fc 2.0-2.2, unification and simplification.}

During this period of development the SU(3) algebra was changed to SU($N$). Several tools for automatic tree-level calculation were added, for example the function \mb{SquareAmplitude}. (Unfortunately, the  documentation was not updated.) All sub-packages were put into one file \(\big(\simeq {{10}^4}\) lines), "FeynCalc2.2beta.m" \footnote{This file is still available upon request}.

\subsubsection*{1993-1996 : \fc 3.0, modularization, typesetting, Operator Product Expansion (OPE)}

Due to the rapidly increasing amount of code, \fc was reorganized in a modular way. The definitions of each function are contained in a package file which is loaded only on demand. For the maintenance of hundreds of packages, totalling 2.5 megabytes, software engineering was needed.

\begin{itemize}

\item
In these years many improvements were made to the code, driven by the work of the author (Rolf Mertig) 
together with Willy van Neerven in perturbative Quantum Chromo Dynamics (QCD).

One effort was to build data bases: Convolutions, integrals, tensor integral transformation
formulae, Feynman rules,
and Feynman parameterizations. 
Applications include 2-loop spin-independent and spin-dependent Altarelli-Parisi splitting
functions \cite{Altarelli:1977zs}.

\item The new typesetting capabilities of \mma 3 (TraditionalForm) were used to substantially
improve the look of the output.
Typesetting rules were added for e.g. \({\overvar{\partial }{\rightarrow}}_{\mu } \multsp \).

\item Code was written to allow new abstract data types, for example for noncommutative algebra
 and for special integrals.

\item QCD tools for the Operator Product Expansion  (OPE)
were added.

\item Automatic Feynman rule derivation (with functional
differentation) was implemented in order to get special Feynman rules
for twist-2 (and higher) operators.

\end{itemize}

\subsubsection*{1997-2000 : \fc 4.0-4.1, QCD and OPE, ChPT, tables}

Another was the package \tarcer, which was initially an independent project, but then integrated
into \fc.  \tarcer \cite{Mertig:1998vk} adds two-loop functionality for propagator-type integrals
using the recurrence relations of Tarasov \cite{Tarasov:1997kx}.

In 2000 maintenance of the package was taken over by Frederik Orellana.
He worked in Chiral Perturbation Theory \cite{Gasser:1984gg} (ChPT) and made some changes, as well
as adding code to \fc in order to support ChPT and effective theories in general, and interfacing
with \fa. Also, first implementations of the 'tHooft-Veltman formulae \cite{'tHooft:1978xw} for
numerical evaluation of the one-loop integrals $B_0, C_0$ and $D_0$ were added. 
