\chaptermark{The FeynCalc Framework}
\chapter{The \fc Framework}

\section{Introduction}
\label{intro}

\fc is a \mma package that provides a framework for doing calculations
in quantum field theory and, within this framework, a collection of utilities
for the more common as well as some more specialized tasks
in such calculations.

%The original idea of \fc was to provide convenient tools for
One typical task is the calculation of
radiative corrections in the Standard Model of particle physics.
The input for \fc, the analytical expressions for the diagrams, can be
entered by hand or can be taken directly from the output of the Feynman diagram generator \fa\ \cite{feynarts} .
The user can provide certain additional  information about the process
under consideration, i.e. the kinematics and the choice of the standard
matrix elements may be defined. Once this is done, \fc performs the
algebraic calculations like tensor algebra, tensor integral decomposition and reduction,
yielding a polynomial in standard matrix elements,  special functions, kinematical
variables and scalars suitable for further numerical evaluation.

\fc also provides calculator-like features.
These features include basic operations like contraction of
tensors, simplification of products of Dirac matrices and trace calculation.
For instance, a Dirac trace is entered
in a notation very similar to that used when doing calculations by hand, and
an answer suitable for further manipulation is returned.

More complex algebraic operations have also been implemented, notably derivation
of polynomials in quantum fields with respect to such fields.

\fc is installed by following the steps below (modify version number to match
the newest release).

\begin{itemize}

\item{Download the file "HighEnergyPhysics-9.0.tar.gz" or
"HighEnergyPhysics-9.0.zip".}

\item{If you already have an old installation and have customized the file "FCConfig.m", back it up.}

\item{Unpack the archive in any of the following places:

\begin{itemize}

\item{Anywhere on your file system. If the location is not on the \mma \mb{\$Path} you
have to load \fc by \mb{<</myfullpathname/HighEnergyPhysics/FeynCalc.m}.}

\item{One of the \mma "Applications" directories: For {\sc Unix} or {\sc GNU/Linux} and
\mma 4.2 or higher, "\~/.Mathematica/Applications/" (the tilde refers to you home directory).
For other operating systems: evaluate \mb{\$UserAddOnsDirectory} or \mb{\$AddOnsDirectory} in \mma.}
\end{itemize}
}

\item{If you've made any customizations in the configuration file "FCConfig.m", merge them from the file you've moved away into the new file.}

\item{Start \mma.}

\item{Choose 'Rebuild Help Index' from the 'Help' menu.}

\item{Load \fc with \mb{<<HighEnergyPhysics`FeynCalc`} or \mb{<<HighEnergyPhysics`FeynCalc`}.}

\end{itemize}



